MS Depression Paper, post replication, started 2022 09 21

### 2022-09-29 msdepression/scripts/MS_Depression_First_Paper_started_20220728/msdepression_n380_started_2022092022_post_replication.Rmd
Add files via upload

@@

#eff size = 0.78 (large)
msdisease_within_versus_outside_depression_network_sums_scaled_by_size_wilcoxon_eff_size <- rstatix::wilcox_effsize(df_empi_dx_network_proportions, formula = proportion_affected ~ Network, paired = T, conf.level = 0.95, ci.type = "perc", nboot = 1000)

>>>>

#within nondepressed group, V=9661, p <2.2*10^-16
msdisease_within_versus_outside_depression_network_nondep_group_sums_scaled_by_size_wilcoxon <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_dep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_nondep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1],paired = TRUE)

#within depressed group, V= 25143, p<2.2*10^-16
msdisease_within_versus_outside_depression_network_dep_group_sums_scaled_by_size_wilcoxon <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_dep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_nondep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2],paired = TRUE)

@@

#effect size within vs outside dep network, eff size = 0.78 (large)
msdisease_within_versus_outside_depression_network_sums_scaled_by_size_wilcoxon_eff_size <- rstatix::wilcox_effsize(df_empi_dx_network_proportions, formula = proportion_affected ~ Network, paired = T, conf.level = 0.95, ci.type = "perc", nboot = 1000)

#effect size dep vs nondep network within nondepressed, eff size = 0.75 (large)
msdisease_within_versus_outside_depression_network_nondep_group_sums_scaled_by_size_wilcoxon_eff_size <- rstatix::wilcox_effsize(df_empi_dx_network_proportions[(df_empi_dx_network_proportions$Diagnosis == "Nondepressed"),], formula = proportion_affected ~ Network, paired = T, conf.level = 0.95, ci.type = "perc", nboot = 1000)

#effect size dep vs dep network within depressed, eff size = 0.80, large
msdisease_within_versus_outside_depression_network_nondep_group_sums_scaled_by_size_wilcoxon_eff_size <- rstatix::wilcox_effsize(df_empi_dx_network_proportions[(df_empi_dx_network_proportions$Diagnosis == "Depressed"),], formula = proportion_affected ~ Network, paired = T, conf.level = 0.95, ci.type = "perc", nboot = 1000)
